\startchapter [title={Counting}]

	\startproposition[title={Basic principle of counting}]
		Suppose two independent experiments are performed, and there are \m{m} possible outcomes of the first experiment and \m{n} possible outcomes of the second experiment. Then the total possible outcomes of of the two experiments combined is \m{m n}.
	\stopproposition
	
	\startproof
		Let \m{(i, j)} denote the case when the first experiment gives the \m{i}th outcome and the second experiment gives the \m{j}th outcome. Enumerating, we get
		\startformula  \startmatrix[n=4]
			\NC  (1, 1)  \NC  (1, 2)  \NC  …  \NC  (1, n)  \NR
			\NC  (2, 1)  \NC  (2, 2)  \NC  …  \NC  (2, n)  \NR
			\NC  ⋮       \NC  ⋮       \NC  ⋱  \NC  ⋮       \NR
			\NC  (m, 1)  \NC  (m, 2)  \NC  …  \NC  (m, n)  \NR
		\stopmatrix	 \stopformula
		Since there are \m{m} rows and \m{n} columns, we have total \m{mn} entries.
	\stopproof

	\startremark
		This can be generalized to a finite number of experiments.
	\stopremark


	\starttheorem [title={Binomial theorem}]
		\startformula
			(x + y)^n = ∑_{k = 0}^n \binom{n}{k} x^k y^{n - k}.
		\stopformula
	\stoptheorem
	
	\startproof [title={Inductive}]
		Homework.
	\stopproof

	\startproof [title={Combinatorial}]
		Consider the product \m{(x_1 + y_1) (x_2 + y_2) ⋯ (x_n + y_n)}.

		First, note that the expansion consists of \m{2^n} terms, each being a product of \m{n} factors.

		Secondly, each product contains either \m{x_j} xor \m{y_j} for each \m{j ∈ [n]}.

		\comment{For example, \m{(x_1 + y_1) (x_2 + y_2) = x_1 x_2 + x_1 y_2 + y_1 x_2 + y_1 y_2}.}

		Now, we can we choose \m{k} of the \m{x_j}s and \m{n - k} of the \m{y_j}s in \m{\binom{n}{k}} ways, so there are precisely those many terms with m{k} \m{x_j}s and \m{n - k} \m{y_j}s in the expansion.

		Finally, letting \m{x_j = x} and \m{y_j = y} for each \m{j ∈ [n]}, we get the result.
	\stopproof

	\startremark
		This can be generalized to a finite number of experiments.
	\stopremark


\stopchapter
